Hierarchical model assessing the impacts of time to detection distribution assumptions on detection probability estimation

### 2016-08-09 Draft.tex
Add some additional comments

@@

\jarad{need to define what we mean by $\pdet$ here.}

\jarad{where's the supplement? I think we should just refer to to the Figures on the supplement just like we refer to papers in the main manuscript and then interpret them.}

@@

We fit the Ovenbird dataset with exponential, gamma, lognormal, and Weibull mixture models.  
For the abundance half of our model, we used four covariates plus two random effects.  
The covariates were: (a) site age, (b) survey year, (c) an indicator of whether the site stock density was over 70\%, and (d) an indicator of whether the site experienced select-/partial-cut logging during the 1990s.  
We associated random effects with each survey year and each stand \jarad{did we define stand previously?}.
For the detection half of our model, we used covariates for: (a) Julian date, (b) time of day, (c) temperature, (d) an indicator of whether it is the observer's first year in the database, and (e) an interaction between (a) and (d) to approximate a new observer's learning curve.  
We associated random effects with each observer.  
Preliminary model fits did not support the inclusion of quadratic terms for any detection covariates.  
We centered and standardized all continuous covariates prior to fitting models.
We ran chains 250,000-375,000 iterations; Geweke diagnostics showed no indication of lack of fit, and effecive sample sizes were over 1000 for all parameters.

>>>>

\jarad{Abstract the data}

@@

\jarad{need to define what we mean by $\pdet$ here since it's definition has changed.}

\jarad{I think we should just refer to to the Figures on the supplement just like we refer to papers in the main manuscript and then interpret them, e.g. Figure S1 shows ...}

@@

We fit the Ovenbird dataset with exponential, gamma, lognormal, and Weibull mixture models.  
For the abundance half of our model, we used four covariates plus two random effects.  
The covariates were: (a) site age, (b) survey year, (c) an indicator of whether the site stock density was over 70\%, and (d) an indicator of whether the site experienced select-/partial-cut logging during the 1990s.  
We associated random effects with each survey year and each stand.
For the detection half of our model, we used covariates for: (a) Julian date, (b) time of day, (c) temperature, (d) an indicator of whether it is the observer's first year in the database, and (e) an interaction between (a) and (d) to approximate a new observer's learning curve.  
We associated random effects with each observer.  
Preliminary model fits did not support the inclusion of quadratic terms for any detection covariates.  
We centered and standardized all continuous covariates prior to fitting models.
We ran chains 250,000-375,000 iterations; Geweke diagnostics showed no indication of lack of fit, and effecive sample sizes were over 1000 for all parameters.
